Evolution Reinforces Cooperation with the Emergence of Self-Recognition Mechanisms: an Empirical Study of Strategies in the Moran process for the Iterated Prisoner's Dilemma

### 2018-07-19 main.tex

One particular family of strategies that has been studied in the literature are
called finite state machines. These mathematical models consist of states
and responses to actions which indicate a next state given an action. In the
context of the IPD, a finite state machine, is a mapping from an arbitrary list
of states and opponent actions (cooperation or defection) to states and an
action (cooperation or defection). For further details,
the reader is referred to~\cite{Ashlock2006, Harper2017}.

@@

@@

>>>>

One particular family of strategies that has been studied in the literature are
called finite state machines. These mathematical models consist of states
and responses to actions which indicate a next state given an action. In the
context of the IPD, a finite state machine, is a mapping from an arbitrary list
of states and opponent actions (cooperation or defection) to states and an
action (cooperation or defection). For further details,
the reader is referred to~\cite{Ashlock2006, AshlockBook, Ashlock2007, Harper2017}.

@@

\bibitem{Ashlock2007}
Wendy Ashlock
\newblock {Why some representations are more cooperative than others for
prisoner's dilemma}
\newblock {\em Foundations of Computational Intelligence, 2007. FOCI 2007. IEEE
symposium on}, 314--321,
  2007.

@@

\bibitem{AshlockBook}
Daniel Ashlock.
\newblock{Evolutionary computation for modeling and optimization},
\newblock{Springer Science \& Business Media}
2006
